Automatically generated NE tagged corpora for English and Hungarian

### 2012-03-25 paper/engNERwiki.tex

There are several ways to increase precision, sentence coverage and to account for peculiarities in the CoNLL guidelines. These are detailed in the next subsections.

>>>>

The following sub-sections describe how the method explained above can be improved to increase precision, sentence coverage and to account for peculiarities in the CoNLL guidelines.
